%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Siddhartha}{Vikram}{ \urlstyle{same}\url{} \\
\href{mailto:siddhartsingh9876@gmail.com}{siddhartsingh9876@gmail.com} | +91-778-584-5447
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{NATIONAL INSITUTE OF}
\subsection{Technology}
\descript{Masters in Computer Application}
\location{Expected May 2019 | Durgapur, West Bengal \\ Cum. GPA: 6.3(3th Sem)}
\sectionsep

\subsection{DDE,Swami Vivekanand}
\subsection{Subharti University}
\descript{Bachelor in Computer Application}
\location{Grad. May 2016 | Allahabad, India}
\location{ 66.70/100 }
\sectionsep

\subsection{Maharishi Vidya Mander}
\descript{ Intermediate Education C.B.S.E}
\location{Grad. May 2013|  Fatehpur, India \\
53.8/100}
\sectionsep

\descript{ High School C.B.S.E}
\location{Grad. May 2011|  Fatehpur, India \\
6.4/10}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/apex1000}{\custombold{apex1000}} \\
LinkedIn://  \href{https://www.linkedin.com/in/apex1000}{\custombold{apex1000}}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Competitive Programming}
(All usernames: apex1000)\\
\location{Peak Ratings:}
\href{https://www.hackerrank.com/apex1000}{Hackerrank}: 81st percentile. \\
\href{https://www.codechef.com/users/apex1000}{Codechef}: 1514(green).\\
\location{Selected Ranks:}
Hackerrank Algorithms: 1987.52 Points.
\sectionsep


\subsection{Programming}
\location{Experience:}
C \textbullet{}  C++ \textbullet{} Python \textbullet{} Javascript \\
 \textbullet{} Django \textbullet{} Rails \textbullet{} AngularJS \\
 \textbullet{} Firebase \textbullet{} RaspberryPI\\
\location{Familiar:}
Flask \textbullet{} Bootstrap \textbullet{} Nokogiri \\
\textbullet{} \LaTeX\ \textbullet{} ASP.net \textbullet{} MySQL\\
\textbullet{} MongoDB \textbullet{} RouterOS \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{ExpertsHub}
\descript{| Software Development Intern(IoT) }
\location{Expected Dec 2016 – Jan 2017 | Pune, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Worked with a Team to develop JIT Application.\\
\item 20 out of 500 applicants chosen to be a Best Intern Award.
\end{tightemize}
\sectionsep

\runsubsection{NIT Durgapur}
\descript{| Research + Software Engineering Intern }
\location{May 2017 – July 2017 | Durgapur, India}
\begin{tightemize}
\item Worked on Real Time Data(Sensor Data). Develop RealTime Dashboard for Data Presentation.
\item Lead Developer in Web Development Team , Government Project (MediaAsia Labs).  
\end{tightemize}
\sectionsep

\runsubsection{NIT Durgapur}
\descript{| Research + Software Engineering Intern }
\location{Dec 2017 – Feb 2018 | Durgapur, India}
\begin{tightemize}
\item Worked on Data Visualization tools in RaspberryPI environments. 
\item Lead Developer in Web Development Team , Government Project (MediaAsia Labs).  
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Project
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Udash}
\descript{| MEAN stack Application }
\location{Dec 2017 – Present}
Discovered Data Visualization tools to present diffrent types of data.  \\
Link to Repo: \textbf{\href{https://github.com/Apex1000/offlineMCS_V.2}{uDASH}}
\sectionsep

\runsubsection{offlineMCS/onlineMCS}
\descript{| Django Firebase}
\location{May 2017 – Dec 2017}
Web Application for data presentation online/offline. Application is hosted on RaspberryPI along with diffrent other Sensor. \\
Link to Repo: \textbf{\href{https://github.com/ItsForkIT/onlinemcs}{onlineMCS}}
\sectionsep

\runsubsection{EmbServices}
\descript{| Rails Firebase Nokogiri }
\location{May 2017 – Present}
Group of scripts used to get data from diffrent Non-APIs data sources. Information is used in diffrent IEEE papers. \\
Link to Repo: \textbf{\href{https://github.com/Apex1000/udash}{ EmbServices}}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{uDASH}
\descript{| Data Visualization Research}
\location{Oct 2017 – Present }
Project based on Data Visualization to present diffrent type of data.
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}
\sectionsep 
\begin{tightemize}
\item Best Intern Award out of 20/500.
\item Lead Developer in Collage Project(ITRA MediaAsia Lab).

\end{tightemize}
\sectionsep


\end{minipage} 
\end{document}